THESIS PROJECT PROPOSAL

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

There are various production modes of Higgs boson like the gluon gluon  fusion(ggF), vector boson fusion(VBF), higgs production 
in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with 
a single top quark and a quark jet(tHq). Each production channel has its own importance to probe the properties and the coupling 
strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggF). As 
bosons like gluons and photons are massless, they do not interact directly with the Higgs boson and processes like ggF or Higgs 
boson decay to pair of photons are not possible at tree level and can only proceed via loop diagrams which involve W boson or top 
quark in the loop. The Higgs boson can also decay to other particles and these decay channels have different branching fractions. 
Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to 
Z boson and a photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put 
upper bounds on dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.

>>>>

There are various production modes of Higgs boson like the gluon gluon  fusion(ggF), vector boson fusion(VBF), Higgs production 
in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with 
a single top quark and a quark jet(tHq). Each production channel has its own importance to probe the properties and the coupling 
strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggF). As 
bosons like gluons and photons are massless, they do not interact directly with the Higgs boson and processes like ggF or Higgs 
boson decay to pair of photons are not possible at tree level and can only proceed via loop diagrams which involve W boson or top 
quark in the loop. The Higgs boson can also decay to other particles and these decay channels have different branching fractions. 
Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to 
Z boson and a photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put 
upper bounds on dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.
